---
title: "module1_v1"
author: "Nelson Tang"
date: "30/09/2020"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


##Data pre-processing 
```{r}
rm(list = ls())
train <- read.table('train2.txt',sep = ',',header = TRUE)
test <- read.table('test2.txt',sep = ',',header = TRUE)

```

##Dealing with Age
```{r}
age <- train$age


##create different feature of age
##Note that : max(age) = 96 , min(age) = NA



age.0to9 = rep(0, nrow(train))
age.10to19 = rep(0, nrow(train))
age.20to29 = rep(0, nrow(train))
age.30to39 = rep(0, nrow(train))
age.40to49 = rep(0, nrow(train))
age.50to59 = rep(0, nrow(train))
age.60to69 = rep(0, nrow(train))
age.70to79 = rep(0, nrow(train))
age.80to89 = rep(0, nrow(train))
age.90to99 = rep(0, nrow(train))
age.missing = rep(0, nrow(train))

#if age is an interval then we define it as mean
for (i in 1:length(age)) {
  if (grepl('-',age[i])) {
    z = strsplit(age[i], '-')
    age[i] = mean (as.numeric(c(z[[1]][1],z[[1]][2])))
  }
}

age <- as.numeric(age)
mu <- mean(age[!is.na(age)])
library(tidyverse)
age = replace_na(age,mu)

#age = as.numeric(age)
for (i in 1:length(age)) {
  if (is.na(age[i]) || age[i] == '') {
    age.missing[i] =1
  }
  else if (0<= as.numeric(age[i]) && as.numeric(age[i])<10) {age.0to9[i] = 1}
  else if (10<=as.numeric(age[i]) && as.numeric(age[i])<20) {age.10to19[i] = 1}
  else if (20<=as.numeric(age[i]) && as.numeric(age[i])<30) {age.20to29[i] = 1}
  else if (30<=as.numeric(age[i]) && as.numeric(age[i])<40) {age.30to39[i] = 1}
  else if (40<=as.numeric(age[i]) && as.numeric(age[i])<49) {age.40to49[i] = 1}
  else if (50<=as.numeric(age[i]) && as.numeric(age[i])<60) {age.50to59[i] = 1}
  else if (60<=as.numeric(age[i]) && as.numeric(age[i])<70) {age.50to59[i] = 1}
  else if (70<=as.numeric(age[i]) && as.numeric(age[i])<80) {age.70to79[i] = 1}
  else if (80<=as.numeric(age[i]) && as.numeric(age[i])<90) {age.80to89[i] = 1}
  else if (90<=as.numeric(age[i]) && as.numeric(age[i])<100) {age.90to99[i] = 1}
}

# all.age <- as.data.frame(cbind(age, age.missing, age.0to9, age.10to19, 
#                                  age.20to29, age.30to39, age.40to49, age.50to59, age.60to69,
                                 # age.70to79, age.80to89, age.90to99))
all.age <- as.data.frame(cbind(age))
```

#dealing with sex
#we convert all features to indictor vriables
```{r}
#we only select those feature both appear in train and test
intersect_feature = intersect(train$sex,test$sex)
intersect_feature

sex = train$sex

sex.38fc4 = rep(0, nrow(train))
sex.8a467 = rep(0, nrow(train))
sex.d516d = rep(0, nrow(train))
sex.f7f7c = rep(0, nrow(train))
sex.missing = rep(0, nrow(train))

for (i in 1:length(sex)) {
  if (grepl('38fc4',sex[i])) {sex.38fc4[i] = 1}
  else if (grepl('8a467',sex[i])) {sex.8a467[i] = 1}
  else if (grepl('d516d',sex[i])) {sex.d516d[i] = 1}
  else if (grepl('f7f7c',sex[i])) {sex.f7f7c[i] = 1}
  else if (is.na(sex[i])) {sex.missing[i] = 1}
}

all.sex <- as.data.frame(cbind( sex.38fc4, sex.8a467, sex.d516d, sex.f7f7c, sex.missing))
new.train <- cbind(all.age,all.sex)
```

#dealing with city 
#we convert all features to indictor vriables
``{r}
city = train$city
city_intersect = intersect(train$city,test$city)
city_intersect
##create a data frame containing all intersect city 
city_matrix = as.data.frame(matrix(ncol = length(city_intersect), nrow = length(city)))

##crreate a array of each feature in city
feature = c()
for (each_city in city_intersect) {feature = append(feature,paste0('city.',each_city))}

colnames(city_matrix) = feature

for (i in 1:length(city)) {
  for (j in 1:length(feature)) {
    if (grepl(city[i],feature[j])) {
      city_matrix[i,j] = 1
    }
    else {city_matrix[i,j] = 0}
  }
}
new.train <- cbind(new.train,city_matrix)
``

##dealing with province
``{r}
province = train$province
province_intersect = intersect(train$province,test$province)
province_intersect
##create a data frame containing all intersect province 
province_matrix = as.data.frame(matrix(ncol = length(province_intersect), nrow = length(province)))

##crreate a array of each feature in province
feature = c()
for (each_province in province_intersect) {feature = append(feature,paste0('province.',each_province))}

colnames(province_matrix) = feature

for (i in 1:length(province)) {
  for (j in 1:length(feature)) {
    if (grepl(province[i],feature[j])) {
      province_matrix[i,j] = 1
    }
    else {province_matrix[i,j] = 0}
  }
}
new.train <- cbind(new.train,province_matrix)
``

##dealing with country

```{r}
country = train$country
country_intersect = intersect(train$country,test$country)
country_intersect
##create a data frame containing all intersect country 
country_matrix = as.data.frame(matrix(ncol = length(country_intersect), nrow = length(country)))

##crreate a array of each feature in country
feature = c()
for (each_country in country_intersect) {feature = append(feature,paste0('country.',each_country))}

colnames(country_matrix) = feature

for (i in 1:length(country)) {
  for (j in 1:length(feature)) {
    if (grepl(country[i],feature[j])) {
      country_matrix[i,j] = 1
    }
    else {country_matrix[i,j] = 0}
  }
}
new.train <- cbind(new.train,country_matrix)
```

##dealing with V1

```{r}
V1 = train$V1
V1_intersect = intersect(train$V1,test$V1)
V1_intersect
##create a data frame containing all intersect V1 
V1_matrix = as.data.frame(matrix(ncol = length(V1_intersect), nrow = length(V1)))

##crreate a array of each feature in V1
feature = c()
for (each_V1 in V1_intersect) {feature = append(feature,paste0('V1.',each_V1))}

colnames(V1_matrix) = feature

for (i in 1:length(V1)) {
  for (j in 1:length(feature)) {
    if (grepl(V1[i],feature[j])) {
      V1_matrix[i,j] = 1
    }
    else {V1_matrix[i,j] = 0}
  }
}
new.train <- cbind(new.train,V1_matrix)
```
##dealing with confirmed
##we convert confirmed date to numeric value


```{r}
confirmed = train$confirmed
for (i in 1:length(confirmed)){
  confirmed[i]=as.POSIXct(confirmed[i], format="%d.%m.%y")
}
confirmed = as.numeric(confirmed)
mu <- mean(confirmed[!is.na(confirmed)])
library(tidyverse)
confirmed = replace_na(confirmed,mu)
new.train <- cbind(new.train,confirmed)
```

#dealing with outcome
#1 = Recovery 0 = unknown
```{r, eval= FALSE}
outcome = train$outcome
for (i in 1:length(outcome)){
  if (outcome[i] == 'Recovery'){
    outcome[i] = 1
  }
  else {outcome[i] = 0}
}
new.train <- cbind(new.train,outcome)
```

##Adding symtoms_number(Chris)

```{r}
symptoms_number = NULL

trim <- function (x) gsub("^\\s+|\\s+$", "", x)
symptoms = trim(train$symptoms)
for (i in 1:dim(train)[1]) {
  x = symptoms[i]
  if(x == ''){
    symptoms_number[i] = 0
  }else {
    symptoms_number[i] = lengths(regmatches(x, gregexpr(";", x))) + 1
  }
}

new.train <- cbind(new.train,symptoms_number)
```

##dealing with sympotoms

```{r}
##1. pre-processiong with text data 
#TODO: (optional) add feature no_symptoms
# train symptoms
train_symptoms=as.data.frame(train$symptoms)
#split string by ';'
library('tidyverse')
train_symptoms=as.data.frame(separate_rows(train_symptoms, 1, sep = ";", convert = FALSE))
colnames(train_symptoms) = c('train_symptoms')


for (i in 1:nrow(train_symptoms)){
  ## TODO: another way to extract feature by particular temp
  if (grepl('fever',train_symptoms[i,1])) {train_symptoms[i,1] = 'fever'}
  
  #remove leading space and trail space
  train_symptoms[i,1] = gsub("^\\s+|\\s+$", "", train_symptoms[i,1])
}

# test symptoms
test_symptoms=as.data.frame(test$symptoms)
#split string by ';'
test_symptoms=as.data.frame(separate_rows(test_symptoms, 1, sep = ";", convert = FALSE))
colnames(test_symptoms) = c('test_symptoms')
for (i in 1:nrow(test_symptoms)){
  ## TODO: another way to extract feature by particular temp
  if (grepl('fever',test_symptoms[i,1])) {test_symptoms[i,1] = 'fever'}
  
  #remove leading space and trail space
  test_symptoms[i,1] = gsub("^\\s+|\\s+$", "", test_symptoms[i,1])
}

```

``{r}
##extract feature from train data
#Find interection of symptoms in train and test
symptoms_intersect=intersect(train_symptoms$train_symptoms,test_symptoms$test_symptoms)
symptoms_intersect

#here we want to remove missing value in intersect array
symptoms_intersect = symptoms_intersect[-4]
symptoms_intersect

symptoms = train$symptoms
##create a data frame containing all intersect V1 
symptoms_matrix = as.data.frame(matrix(ncol = length(symptoms_intersect), nrow = length(symptoms)))

##crreate a array of each feature in V1
feature = c()
for (each_symptoms in symptoms_intersect) {feature = append(feature,paste0('symptoms.',each_symptoms))}

colnames(symptoms_matrix) = feature

for (i in 1:length(symptoms)) {
  for (j in 1:length(feature)) {
    if (grepl(symptoms_intersect[j],symptoms[i])) {
      symptoms_matrix[i,j] = 1
    }
    else {symptoms_matrix[i,j] = 0}
  }
}
##add duration and symptoms.feature in new.train
``


duration = train$duration
new.train <- cbind(new.train,symptoms_matrix,duration)
``

```{r}
duration = train$duration
new.train <- cbind(new.train,duration)
write.table(new.train, file = 'cleaned_train_AoTang.txt', sep= ',')

```

