---
title: "STAT440 Data_Preprocessing"
author: "Ao Tang (301297684),Xiaoliang Zhang (301297782),Zhengtang Lin (301310788),Junchao Liu (301299668)"
date: "16/10/2020"
output: pdf_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Data pre-processing 
```{r}
rm(list = ls())
train <- read.table('train2.txt',sep = ',',header = TRUE)
test <- read.table('test2.txt',sep = ',',header = TRUE)
```

## Combine the two data frame
```{r}
train$is_train = T
test$is_train = F
train$Id = NA
train$outcome = NULL
test$duration = NA
combined = rbind(train,test)
```

## Dealing with Age
```{r}
age <- combined$age

#if age is an interval then we define it as mean
for (i in 1:length(age)) {
  if (grepl('-',age[i])) {
    z = strsplit(age[i], '-')
    age[i] = mean (as.numeric(c(z[[1]][1],z[[1]][2])))
  }
}

age <- as.numeric(age)
mu <- mean(age[!is.na(age)])
library(tidyverse)
age = replace_na(age,mu)

#age = as.numeric(age)
for (i in 1:length(age)) {
  if (is.na(age[i]) || age[i] == '') {
    age.missing[i] =1
  }
}

all.age <- as.data.frame(cbind(age))
```

# dealing with sex
# we convert all features to indictor vriables
# TODO: <4 create a dummy variable call others
```{r}
#we only select the feature that appears >4 times in training set
sex = combined$sex
sex_union = union(train$sex,test$sex)
sex_union = c(sex_union,'others')
##create a data frame containing all union sex
sex_matrix = as.data.frame(matrix(ncol = length(sex_union), nrow = length(sex)))

##crreate a array of each feature in sex
feature = c()
for (each_sex in sex_union) {feature = append(feature,paste0('sex.',each_sex))}

colnames(sex_matrix) = feature

for (i in 1:length(sex)) {
  for (j in 1:length(feature)) {
    if (grepl(sex[i],feature[j])) {
      sex_matrix[i,j] = 1
    }
    else {sex_matrix[i,j] = 0}
  }
}
low_index = apply(sex_matrix, 2, sum) < 8
for (i in 1:length(sex)) {
  if (sum(sex_matrix[i,low_index])>0){
    sex_matrix[i,'sex.others'] = 1
  }
}
new_low_index = apply(sex_matrix, 2, sum) < 8
sex_matrix[,new_low_index] = NULL
new.combined <- cbind(all.age, sex_matrix)
```

# dealing with city 
# we convert all features to indictor vriables
```{r,eval=False}
city = combined$city
city_union = union(train$city,test$city)
city_union = c(city_union,'others')
##create a data frame containing all intersect city
city_matrix = as.data.frame(matrix(ncol = length(city_union), nrow = length(city)))

##crreate a array of each feature in city
feature = c()
for (each_city in city_union) {feature = append(feature,paste0('city.',each_city))}

colnames(city_matrix) = feature

for (i in 1:length(city)) {
  for (j in 1:length(feature)) {
    if (grepl(city[i],feature[j])) {
      city_matrix[i,j] = 1
    }
    else {city_matrix[i,j] = 0}
  }
}

low_index = apply(city_matrix, 2, sum) < 8
for (i in 1:length(city)) {
  if (sum(city_matrix[i,low_index])>0){
    city_matrix[i,'city.others'] = 1
  }
}
new_low_index = apply(city_matrix, 2, sum) < 8
city_matrix[,new_low_index] = NULL

new.combined <- cbind(new.combined,city_matrix)
```


## dealing with province
# TODO: <4 create a dummy variable call others
```{r}
#we only select the feature that appears >4 times in training set
province = combined$province
province_union = union(train$province,test$province)
province_union = c(province_union,'others')
##create a data frame containing all union province
province_matrix = as.data.frame(matrix(ncol = length(province_union), nrow = length(province)))

##crreate a array of each feature in province
feature = c()
for (each_province in province_union) {feature = append(feature,paste0('province.',each_province))}

colnames(province_matrix) = feature

for (i in 1:length(province)) {
  for (j in 1:length(feature)) {
    if (grepl(province[i],feature[j])) {
      province_matrix[i,j] = 1
    }
    else {province_matrix[i,j] = 0}
  }
}
low_index = apply(province_matrix, 2, sum) < 8
for (i in 1:length(province)) {
  if (sum(province_matrix[i,low_index])>0){
    province_matrix[i,'province.others'] = 1
  }
}
new_low_index = apply(province_matrix, 2, sum) < 8
province_matrix[,new_low_index] = NULL

new.combined <- cbind(new.combined,province_matrix)
```

## dealing with country
# TODO: <4 create a dummy variable call others
```{r}
#we only select the feature that appears >4 times in training set
country = combined$country
country_union = union(train$country,test$country)
country_union = c(country_union,'others')
##create a data frame containing all union country 
country_matrix = as.data.frame(matrix(ncol = length(country_union), nrow = length(country)))

##crreate a array of each feature in country
feature = c()
for (each_country in country_union) {feature = append(feature,paste0('country.',each_country))}

colnames(country_matrix) = feature

for (i in 1:length(country)) {
  for (j in 1:length(feature)) {
    if (grepl(country[i],feature[j])) {
      country_matrix[i,j] = 1
    }
    else {country_matrix[i,j] = 0}
  }
}
low_index = apply(country_matrix, 2, sum) < 8
for (i in 1:length(country)) {
  if (sum(country_matrix[i,low_index])>0){
    country_matrix[i,'country.others'] = 1
  }
}
new_low_index = apply(country_matrix, 2, sum) < 8
country_matrix[,new_low_index] = NULL

new.combined <- cbind(new.combined,country_matrix)
```

## dealing with V1
# TODO: <4 create a dummy variable call others
```{r}
#we only select the feature that appears >4 times in training set
V1 = combined$V1
V1_union = union(train$V1,test$V1)
V1_union = c(V1_union,'others')
##create a data frame containing all union V1 
V1_matrix = as.data.frame(matrix(ncol = length(V1_union), nrow = length(V1)))

##crreate a array of each feature in V1
feature = c()
for (each_V1 in V1_union) {feature = append(feature,paste0('V1.',each_V1))}

colnames(V1_matrix) = feature

for (i in 1:length(V1)) {
  for (j in 1:length(feature)) {
    if (grepl(V1[i],feature[j])) {
      V1_matrix[i,j] = 1
    }
    else {V1_matrix[i,j] = 0}
  }
}
low_index = apply(V1_matrix, 2, sum) < 8
for (i in 1:length(V1)) {
  if (sum(V1_matrix[i,low_index])>0){
    V1_matrix[i,'V1.others'] = 1
  }
}
new_low_index = apply(V1_matrix, 2, sum) < 8
V1_matrix[,new_low_index] = NULL

new.combined <- cbind(new.combined,V1_matrix)
```

## dealing with confirmed
## we convert confirmed date to numeric value
```{r}
confirmed = combined$confirmed
for (i in 1:length(confirmed)){
  confirmed[i]=as.POSIXct(confirmed[i], format="%d.%m.%y")
}
confirmed = as.numeric(confirmed)
mu <- mean(confirmed[!is.na(confirmed)])
library(tidyverse)
confirmed = replace_na(confirmed,mu)
new.combined <- cbind(new.combined,confirmed)
```

## dealing with sympotoms(two features)
```{r}
##1. pre-processiong with text data
#TODO: (optional) add feature no_symptoms
# train symptoms
train_symptoms=as.data.frame(combined$symptoms)
#split string by ';'
library('tidyverse')
train_symptoms=as.data.frame(separate_rows(train_symptoms, 1, sep = ";", convert = FALSE))
colnames(train_symptoms) = c('train_symptoms')


for (i in 1:nrow(train_symptoms)){
  ## TODO: another way to extract feature by particular temp
  if (grepl('fever',train_symptoms[i,1])) {train_symptoms[i,1] = 'fever'}

  #remove leading space and trail space
  train_symptoms[i,1] = gsub("^\\s+|\\s+$", "", train_symptoms[i,1])
}

# test symptoms
test_symptoms=as.data.frame(test$symptoms)
#split string by ';'
test_symptoms=as.data.frame(separate_rows(test_symptoms, 1, sep = ";", convert = FALSE))
colnames(test_symptoms) = c('test_symptoms')
for (i in 1:nrow(test_symptoms)){
  ## TODO: another way to extract feature by particular temp
  if (grepl('fever',test_symptoms[i,1])) {test_symptoms[i,1] = 'fever'}

  #remove leading space and trail space
  test_symptoms[i,1] = gsub("^\\s+|\\s+$", "", test_symptoms[i,1])
}


```

```{r}
##extract feature from train data
#Find interection of symptoms in train and test
symptoms_intersect=intersect(train_symptoms$train_symptoms,test_symptoms$test_symptoms)

#here we want to remove missing value in intersect array
symptoms_intersect = symptoms_intersect[-4]

symptoms = combined$symptoms
##create a data frame containing all intersect V1
symptoms_matrix = as.data.frame(matrix(ncol = length(symptoms_intersect), nrow = length(symptoms)))

##crreate a array of each feature in V1
feature = c()
for (each_symptoms in symptoms_intersect) {feature = append(feature,paste0('symptoms.',each_symptoms))}

colnames(symptoms_matrix) = feature

for (i in 1:length(symptoms)) {
  for (j in 1:length(feature)) {
    if (grepl(symptoms_intersect[j],symptoms[i])) {
      symptoms_matrix[i,j] = 1
    }
    else {symptoms_matrix[i,j] = 0}
  }
}
##keeps only fever and cough
##add duration and symptoms.feature in new.train
duration = combined$duration
new.combined <- cbind(new.combined,symptoms_matrix[,c(4,5)],duration)
```


## dealing with sympotoms(lots of features)
```{r}
# ##1. pre-processiong with text data 
# #TODO: (optional) add feature no_symptoms
# # train symptoms
# train_symptoms=as.data.frame(train$symptoms)
# #split string by ';'
# library('tidyverse')
# train_symptoms=as.data.frame(separate_rows(train_symptoms, 1, sep = ";", convert = FALSE))
# colnames(train_symptoms) = c('train_symptoms')
# 
# 
# for (i in 1:nrow(train_symptoms)){
#   ## TODO: another way to extract feature by particular temp
#   if (grepl('fever',train_symptoms[i,1])) {train_symptoms[i,1] = 'fever'}
#   
#   #remove leading space and trail space
#   train_symptoms[i,1] = gsub("^\\s+|\\s+$", "", train_symptoms[i,1])
# }
# 
# # test symptoms
# test_symptoms=as.data.frame(test$symptoms)
# #split string by ';'
# test_symptoms=as.data.frame(separate_rows(test_symptoms, 1, sep = ";", convert = FALSE))
# colnames(test_symptoms) = c('test_symptoms')
# for (i in 1:nrow(test_symptoms)){
#   ## TODO: another way to extract feature by particular temp
#   if (grepl('fever',test_symptoms[i,1])) {test_symptoms[i,1] = 'fever'}
#   
#   #remove leading space and trail space
#   test_symptoms[i,1] = gsub("^\\s+|\\s+$", "", test_symptoms[i,1])
# }
# 
# 
# ```
# 
# ```{r}
# ##extract feature from train data
# #Find interection of symptoms in train and test
# symptoms_intersect=intersect(train_symptoms$train_symptoms,test_symptoms$test_symptoms)
# symptoms_intersect
# 
# #here we want to remove missing value in intersect array
# symptoms_intersect = symptoms_intersect[-4]
# symptoms_intersect
# 
# symptoms = combined$symptoms
# ##create a data frame containing all intersect V1 
# symptoms_matrix = as.data.frame(matrix(ncol = length(symptoms_intersect), nrow = length(symptoms)))
# 
# ##crreate a array of each feature in V1
# feature = c()
# for (each_symptoms in symptoms_intersect) {feature = append(feature,paste0('symptoms.',each_symptoms))}
# 
# colnames(symptoms_matrix) = feature
# 
# for (i in 1:length(symptoms)) {
#   for (j in 1:length(feature)) {
#     if (grepl(symptoms_intersect[j],symptoms[i])) {
#       symptoms_matrix[i,j] = 1
#     }
#     else {symptoms_matrix[i,j] = 0}
#   }
# }
# ##add duration and symptoms.feature in new.train
# duration = combined$duration
# new.combined <- cbind(new.combined,symptoms_matrix,duration)
```


# Export test data
```{r}
train_ind = 1:nrow(train)
new.test = new.combined[-train_ind,] %>% select(-duration)
write.table(new.test, file = 'cleaned_test.txt', sep= ',')
```

# Export train data
```{r}
new.train = new.combined[train_ind,]
pre_model = lm(duration~age+confirmed,data = new.train)

age = new.train$age + 1
confirmed = new.train$confirmed+ 3600
new_data =as.data.frame(cbind(confirmed,age))
pred = predict(pre_model, new_data)


train_combined = new.train
train_combined$age = new_data$age
train_combined$confirmed = new_data$confirmed
train_combined$duration = pred

train_combined = rbind(new.train,train_combined)

write.table(train_combined, file = 'cleaned_train.txt', sep= ',')
```


