---
title: "Untitled"
author: "Ao Tang"
date: "2020/10/6"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
rm(list = ls())
train <- read.table('train2.txt',sep = ',',header = TRUE, fill = TRUE)
test <- read.table('test2.txt',sep = ',',header = TRUE, fill = TRUE)

train_chris <- read.table('cleaned_train.csv',sep = ',',header = TRUE, fill = TRUE)
test_chris <- read.table('cleaned_test.csv',sep = ',',header = TRUE, fill = TRUE)

train_ao <- read.table('cleaned_train.txt',sep = ',',header = TRUE, fill = TRUE)
test_ao <- read.table('cleaned_test.txt',sep = ',',header = TRUE, fill = TRUE)
```


```{r}
###merge add city 
temp = as.data.frame(table(train$city))
most_freq = temp[order(-temp$Freq),]
most_freq[1:5,1]

train_chris$city.38fc4 = train_ao$city.38fc4
train_chris$city.6d709 = train_ao$city.6d709
train_chris$city.247e5 = train_ao$city.247e5
train_chris$city.d7cac = train_ao$city.d7cac
train_chris$city.2720c = train_ao$city.2720c
```
```{r}
###merge add country

temp = as.data.frame(table(train$country))
most_freq = temp[order(-temp$Freq),]
most_freq[1:5,1]

train_chris$country.59dcd = train_ao$country.59dcd
train_chris$country.fb9d7 = train_ao$country.fb9d7
train_chris$country.c263d = train_ao$country.c263d
train_chris$country.d019a = train_ao$country.d019a
train_chris$country.38fc4 = train_ao$country.38fc4
```


```{r}
###merge add country

temp = as.data.frame(table(train$V1))
most_freq = temp[order(-temp$Freq),]
most_freq[1:5,1]

train_chris$V1.b6ab9 = train_ao$V1.b6ab9
train_chris$V1.35843 = train_ao$V1.35843
train_chris$V1.d68ec = train_ao$V1.d68ec
train_chris$V1.dd554 = train_ao$V1.dd554
train_chris$V1.10775 = train_ao$V1.10775


train_chris$symptoms.fever = train_ao$symptoms.fever
train_chris$symptoms.cough = train_ao$symptoms.cough
```


##we convert confirmed date to numeric value
```{r}
confirmed = train$confirmed
for (i in 1:length(confirmed)){
  confirmed[i]=as.POSIXct(confirmed[i], format='%d.%m.%Y')
  if (is.na(confirmed[i])){confirmed[i] = 'null'}
  }
confirmed = as.numeric(confirmed)
mu <- mean(confirmed[!is.na(confirmed)])
library(tidyverse)
confirmed = replace_na(confirmed,mu)
train_chris$confirmed=confirmed
```

#extract extra feature: 
```{r}
#confirmed = replace_na(confirmed,mu)
#train_chris$diff_day = difftime(strptime(train$confirmed, , format="%d.%m.%Y"),strptime('01.01.2020' , format="%d.%m.%Y"), units = 'days')
```





test set 
---
```{r}
###merge add city 
temp = as.data.frame(table(test$city))
most_freq = temp[order(-temp$Freq),]
most_freq[1:5,1]

test_chris$city.38fc4 = test_ao$city.38fc4
test_chris$city.6d709 = test_ao$city.6d709
test_chris$city.247e5 = test_ao$city.247e5
test_chris$city.d7cac = test_ao$city.d7cac
test_chris$city.2720c = test_ao$city.2720c
```
```{r}
###merge add country

temp = as.data.frame(table(test$country))
most_freq = temp[order(-temp$Freq),]
most_freq[1:5,1]

test_chris$country.59dcd = test_ao$country.59dcd
test_chris$country.fb9d7 = test_ao$country.fb9d7
test_chris$country.c263d = test_ao$country.c263d
test_chris$country.d019a = test_ao$country.d019a
test_chris$country.38fc4 = test_ao$country.38fc4
```


```{r}
###merge add country

temp = as.data.frame(table(test$V1))
most_freq = temp[order(-temp$Freq),]
most_freq[1:5,1]

test_chris$V1.b6ab9 = test_ao$V1.b6ab9
test_chris$V1.35843 = test_ao$V1.35843
test_chris$V1.d68ec = test_ao$V1.d68ec
test_chris$V1.dd554 = test_ao$V1.dd554
test_chris$V1.10775 = test_ao$V1.10775


test_chris$symptoms.fever = test_ao$symptoms.fever
test_chris$symptoms.cough = test_ao$symptoms.cough
```


##we convert confirmed date to numeric value
```{r}
confirmed = test$confirmed
for (i in 1:length(confirmed)){
  confirmed[i]=as.POSIXct(confirmed[i], format="%d.%m.%Y")
  if (is.na(confirmed[i])){confirmed[i] = 'null'}
  }
confirmed = as.numeric(confirmed)
mu <- mean(confirmed[!is.na(confirmed)])
library(tidyverse)
confirmed = replace_na(confirmed,mu)
test_chris$confirmed=confirmed
```

#extract extra feature: 
```{r}
#confirmed = replace_na(confirmed,mu)
#test_chris$diff_day = difftime(strptime(test$confirmed, , format="%d.%m.%Y"),strptime('01.01.2020', format="%d.%m.%Y"), units = 'days')
```







```{r}
pre_model = lm(duration~age+confirmed+symptoms_number,data = train_chris)
pre_model

age = train_chris$age+ 1
confirmed = train_chris$confirmed+ 3600
symptoms_number = train_chris$symptoms_number+ 1 

new_data =as.data.frame(cbind(confirmed,age,symptoms_number))

pred1 = predict(pre_model, new_data)
pred1

new_train = train_chris
new_train$age = new_data$age
new_train$confirmed = new_data$confirmed
new_train$duration = pred1

new_train = rbind(train_chris,new_train)
```

```{r}
library(randomForest)
rf1 = randomForest(duration ~ ., data = new_train)
pred2 = predict(rf1, test_chris)
pred2
```


```{r}

new_train= subset(new_train, select = -c(country,V1))
test_chris= subset(test_chris, select = -c(country,V1))
model1  = lm(duration~.,data = new_train)
pred3 = predict(model1, test_chris)
pred3
```

```{r}
##TODO BUG: train_ao only have 200+ row, need expand to 400+
rf2 = randomForest(duration ~ ., data = train_ao)
pred4 = predict(rf2, test_ao)
pred4
```


```{r}
pred = 0.3*pred2 + 0.4*pred3 + 0.3*pred4
pred
```

#### 4.33055

```{r}
kaggle = read.table(file = 'baseline2.txt', sep = ',', header = T, row.names = NULL)

kaggle$duration = pred

write.table(kaggle, file = 'kaggle1.txt', sep = ',', quote = F, row.name = FALSE)
```


Done by Chris On Oct.07
```{r lm}
# test for best linear model
train = new_train
train$month = NULL
train$sex = NULL
test = test_chris
test$month = NULL
test$sex = NULL


initial.1 <- lm(data=train, formula = duration~ 1)
final.1 <- lm(data=train, formula=duration~.)

step1 <- step(object=initial.1, scope=list(upper=final.1), 
              k = log(nrow(train)))

MSE.matrix = matrix(NA,nrow = 200,ncol = 2)
colnames(MSE.matrix) <- c("MSE","MSPE")
for (r in 1:200) {
  # print(paste0(r," in ",200))
  train_index = sample(1:nrow(train),0.8*nrow(train))
  train_data = train[train_index,]
  valid_data = train[-train_index,]
  # Fit model
  model.linear = lm(duration ~ confirmed + symptoms_number+ age,data = train_data)
  # MSE of the train data
  MSE.matrix[r,1] = mean((predict(model.linear,data = train_data) - train_data$duration)^2)
  # MSE of the valid data
  MSE.matrix[r,2] = mean((predict(model.linear,newdata = valid_data) - valid_data$duration)^2)
  # Age: 1
  # confirmed: 25
  # symptoms_number: 26
  # Sex: 2:5
  # country: 7:16
  # V1: 17:24
}
print(paste0("mean = ", apply(MSE.matrix,2,mean),", sd = ",apply(MSE.matrix,2,sd)))

kaggle = read.table(file = 'baseline2.txt', sep = ',', header = T, row.names = NULL)
kaggle$duration  = predict(step1,newdata = test)
write.table(kaggle, file = 'kaggle1.txt', sep = ',', quote = F, row.name = FALSE)



```

Knn performes very bad in this data using the whold
``{r knn}
# Test for knn
Knn_vector = rep(NA,400)
Knn_matrix = matrix(NA,nrow = 100,ncol = 2)
for (i in 1:100) {
  print(paste0(i," of ",100))
  for(r in 1:400){
    train_index = sample(1:nrow(train),0.8*nrow(train))
    train_data = train[train_index,]
    valid_data = train[-train_index,]
    Knn_vector[r] = mean((as.numeric(knn(train = train_data[,-4], test = valid_data[,-4],cl = train_data[,'duration',drop=TRUE], k=i)) - valid_data$duration)^2)
  }
  Knn_matrix[i,] = c(i,mean(Knn_vector))
}

as.numeric(knn(train = train[,-3], test = test[,-1],cl = train[,'duration',drop=TRUE], k=100))


``

Gradient Boosting Of Regression Trees in R
```{r }
library(caret);library(gbm)

grid<-expand.grid(.n.trees=seq(100,500,by=200),.interaction.depth=seq(1,4,by=1),.shrinkage=c(.001,.01,.1),
                  .n.minobsinnode=10)
control<-trainControl(method = "CV")

gbm.train<-train(duration ~ .,data=train_data,method='gbm',trControl=control,tuneGrid=grid)
gbm.train
```

```{r }
library(caret);library(gbm)

grid<-expand.grid(.n.trees=seq(100,500,by=200),.interaction.depth=seq(1,4,by=1),.shrinkage=c(.001,.01,.1),
                  .n.minobsinnode=10)
control<-trainControl(method = "CV")

gbm.train<-train(duration ~ symptoms_number + confirmed,data=train_data,method='gbm',trControl=control,tuneGrid=grid)
gbm.train
```


```{r best model}
model.boost <- gbm(duration ~ symptoms_number + confirmed, data=train_data,n.trees = 500,interaction.depth = 1,shrinkage = 0.01,distribution = 'gaussian')
gbm.test<-predict(model.boost,newdata = valid_data,n.trees = 500)
gbm.resid<- gbm.test-valid_data$duration
mean(gbm.resid^2)

model.boost <- gbm(duration ~ confirmed + symptoms_number + V1.10775 + country.38fc4,data=train,n.trees = 500,interaction.depth = 1,shrinkage = 0.01,distribution = 'gaussian')
pred5<-predict(model.boost,newdata = test,n.trees = 500)
kaggle = read.table(file = 'baseline2.txt', sep = ',', header = T, row.names = NULL)
kaggle$duration = pred5
write.table(kaggle, file = 'kaggle1.txt', sep = ',', quote = F, row.name = FALSE)
```


```{r ensemble model1}
model1 = lm(duration ~ confirmed + symptoms_number + V1.10775 + country.38fc4, data = train_data)
ensemble.pred1 = predict(model1,newdata = valid_data)
```

```{r ensemble model2}
model2 = lm(duration ~ ., data = train_data)
ensemble.pred2 = predict(model2,newdata = valid_data)
```

```{r ensemble model3}
model3 = randomForest(duration ~ .,data = train_data)
ensemble.pred3 = predict(model3,newdata =valid_data)
```

```{r ensemble model4}
model4 <- gbm(duration ~ .,data=train_data,n.trees = 300,interaction.depth = 3,shrinkage = 0.01,distribution = 'gaussian')
ensemble.pred4 <- predict(model4,newdata = valid_data,n.trees = 300)
```

```{r ensemble model5}
model5 <- gbm(duration ~ age+confirmed+symptoms_number,data=train_data,n.trees = 500,interaction.depth = 1,shrinkage = 0.01,distribution = 'gaussian')
ensemble.pred5 <- predict(model5,newdata = valid_data,n.trees = 500)

```


```{r ensemble coef}
ensemble_matrix = cbind(ensemble.pred1,ensemble.pred2,ensemble.pred3,ensemble.pred4,ensemble.pred5)
ensemble_model = lm(valid_data$duration~ensemble_matrix-1)
ensemble_coef = ensemble_model$coefficients
```

```{r final model}
final.model1 = lm(duration ~ confirmed + symptoms_number + V1.10775 + country.38fc4, data = train)
final.model2 = lm(duration ~ ., data = train)
final.model3 = randomForest(duration ~ .,data = train)
final.model4 <- gbm(duration ~ .,data=train,n.trees = 300,interaction.depth = 3,shrinkage = 0.01,distribution = 'gaussian')
final.model5 <- gbm(duration ~ age+confirmed+symptoms_number,data=train,n.trees = 500,interaction.depth = 1,shrinkage = 0.01,distribution = 'gaussian')
final.pred1 = predict(final.model1,newdata=test)
final.pred2 = predict(final.model2,newdata=test)
final.pred3 = predict(final.model3,newdata=test)
final.pred4 = predict(final.model4,newdata=test)
final.pred5 = predict(final.model5,newdata=test)
final_prediction = cbind(final.pred1,final.pred2,final.pred3,final.pred4,final.pred5) %*% ensemble_coef

kaggle = read.table(file = 'baseline2.txt', sep = ',', header = T, row.names = NULL)
kaggle$duration = final_prediction
write.table(kaggle, file = 'kaggle1.txt', sep = ',', quote = F, row.name = FALSE)
```