---
title: "DataInspection"
author: "chris"
date: "09/10/2020"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r read data}
rm(list =ls())
train <- read.table('~/Documents/GitHub/stat440-Covid-19/ChrisNew/train2.txt',sep = ',',header = TRUE, fill = TRUE)
```

##Dealing with Age
```{r}
age <- train$age
##create different feature of age
##Note that : max(age) = 96 , min(age) = NA
age.missing = rep(0, nrow(train))

#if age is an interval then we define it as mean
for (i in 1:length(age)) {
  if (grepl('-',age[i])) {
    z = strsplit(age[i], '-')
    age[i] = mean (as.numeric(c(z[[1]][1],z[[1]][2])))
  }
}

age <- as.numeric(age)
mu <- mean(age[!is.na(age)])
library(tidyverse)
age = replace_na(age,mu)

#age = as.numeric(age)
for (i in 1:length(age)) {
  if (is.na(age[i]) || age[i] == '') {
    age.missing[i] =1
  }
}

train$age = age
```

##we convert confirmed date to numeric value
```{r}
confirmed = train$confirmed
for (i in 1:length(confirmed)){
  confirmed[i]=as.POSIXct(confirmed[i], format='%d.%m.%Y')
  if (is.na(confirmed[i])){confirmed[i] = 'null'}
  }
confirmed = as.numeric(confirmed)
mu <- mean(confirmed[!is.na(confirmed)])
library(tidyverse)
confirmed = replace_na(confirmed,mu)
train$confirmed=confirmed
```

Adding symptoms_number
```{r}
symptoms_number = NULL

trim <- function (x) gsub("^\\s+|\\s+$", "", x)
symptoms = trim(train$symptoms)
for (i in 1:dim(train)[1]) {
  x = symptoms[i]
  if(x == ''){
    symptoms_number[i] = 0
  }else {
    symptoms_number[i] = lengths(regmatches(x, gregexpr(";", x))) + 1
  }
}

train <- cbind(train,symptoms_number)
```

Variable age
```{r}
plot(train$age,train$duration)
summary(lm(duration~age,data=train))
```
Conclusion: Age is not related to duration, Multiple R-squared:  0.01026,	Adjusted R-squared:  0.005696 

Variable Sex
```{r}
table(as.factor(train$sex))
plot(as.factor(train$sex),train$duration)
summary(lm(duration~sex,data=train))
```
Conclusion: Age is not related to duration, Multiple R-squared:  0.02064,	Adjusted R-squared:  0.00233 

Variable Country
```{r}
table(as.factor(train$country))
plot(as.factor(train$country),train$duration,las=2)
summary(lm(duration~country,data=train))
```
Conclusion: Country is a bit better than Sex and Age, Multiple R-squared:  0.09577,	Adjusted R-squared:  0.04771 

Variable V1
```{r}
table(as.factor(train$V1))
plot(as.factor(train$V1),train$duration,las=2)
summary(lm(duration~V1,data=train))
```
Conclusion: V1 is a bit better than the previous three but lower R-square, Multiple R-squared:0.08332,	Adjusted R-squared:  0.03925 

Variable confirmed
```{r}
plot(train$confirmed,train$duration,las=2)
summary(lm(duration~confirmed,data=train))
```
Conclusion: confirmed is an useful variable, Multiple R-squared:  0.09297,	Adjusted R-squared:  0.08879

Variable province
```{r}
table(as.factor(train$province))
plot(as.factor(train$province),train$duration,las=2)
summary(lm(duration~province,data=train))
```
Conclusion: province mostly p-value > 0.05,but the highest R-squared, Multiple R-squared: 0.2799,	Adjusted R-squared: 0.123 

Variable city
```{r}
table(as.factor(train$city))
plot(as.factor(train$city),train$duration,las=2)
summary(lm(duration~city,data=train))
```
Conclusion: City not considerable, Multiple R-squared:  0.4149,	Adjusted R-squared:  -0.1389 

Variable Symptoms_number
```{r}
plot(train$symptoms_number,train$duration,las=2)
summary(lm(duration~symptoms_number,data=train))
```
Conclusion: Symptoms_number is useful(p<0.05), but extremely low R-squared.Multiple R-squared:  0.0195,	Adjusted R-squared:  0.01498 

```{r BIC}
train$symptoms = NULL
train$outcome = NULL
initial.1 <- lm(formula=duration~ 1,data=train)
final.1 <- lm(formula=duration~.,data=train)

step1 <- step(object=initial.1, scope=list(upper=final.1))

```
